### 2019-12-16 chX_acknowledgements.tex
update thesis

Because relaxing is as important as work,\\a special thanks to a selection of the friends and family.
Laure, Michael, Jasper \& Lize, thank you for the haut cuisine fun veggie nights.
Joke, Niels \& Kai, thank you for exploring dungeons with trolls and lizards together.
Marta, Jan, Tristan \& Rafaël, thank you for the many tasty brunches and classy parties.
Mara Marrainne, Sepperd \& Alice, thank you for all\\the unforgettable family moments with our cute kids.
Daan, Mieke \& Lou, thank you for taking matters in your own hands\\and upgrading our friendship status into family.
Sophie and Marc, thank you for entertaining Caro\\while Elias, Charlotte and I play Minecraft together. 
Bart, thank you for being such a good friend\\and listening to me when I needed it the most.
Miriam, thank you for always being there for us,\\during the good times but also during times of need.
As part of our family, there will always be a spot for you in our house.\\Let it be a while until one of us has to organise another reception.
Cedric, no time difference or distance can keep us apart,\\or change our habit of forgetting the world around us during our gaming and conversations. 
놀라운 사람과 최고의 친구가되어 주셔서 감사합니다
Big hugs for my family who supported me (Vanessa, Marilou, Franco, Alain,\\Luc, Malika, Sien, Silke, Liam, Anne, Patrick, Evelyne, Stefaan, Arne, Laure, 
Paul, Tania, Dorian, Steven, Joke, Lukas, Lise), and often had to miss me at family parties.
To mama and papa Jean Paul, thank you for all your love.\\You gave me a carefree youth and a good set of morals,
and allowed me to study for as long as I liked.\\For all these things and so much more, I can never repay you.
Papa Chris, I always enjoy talking to you, such as the countless\\chess games that we played, and the late night discussions by my bedside.
You made me think for myself and have an opinion of my own.\\At the right time, I will pass on the torch to Remi.
Victor, you're the most adventurous of us three brothers.\\Maybe you don't know yet what life will bring, and that's okay. None of us do.
I enjoy driving other people absolutely nuts with our crazy talk.\\Thanks for all the memes :)
Hendrik, as the one who I always looked up to, I blame you for getting me interested\\in computers. With you taking computers apart on the table, how could I resist.
I know you paid dearly for this, though, since you would continuously have to\\repair the \textit{Windows Me} installation that I just destroyed.
Ingeborg, Elke and Gallina, thank you for your hospitality and tasty food.\\You are all amazing women
for all I know, dealing with a Cannoodt,\\requires a special kind of patience.
Go to the next chapter for more acknowledgements.

>>>>

Because relaxing is as important as work,\\a special thanks to a selection of the friends and family.
Laure, Michael, Jasper \& Lize, thank you for the haut cuisine fun veggie nights.
Joke, Niels \& Kai, thank you for exploring dungeons with trolls and lizards together.
Marta, Jan, Tristan \& Rafaël, thank you for the many tasty brunches and classy parties.
Mara Marrainne, Sepperd \& Alice, thank you for all\\the unforgettable family moments with our cute kids.
Daan, Mieke \& Lou, thank you for taking matters in your own hands\\and upgrading our friendship status into family.
Sophie and Marc, thank you for entertaining Caro\\while Elias, Charlotte and I play Minecraft together. 
Bart, thank you for being such a good friend\\and listening to me when I needed it the most.
Miriam, thank you for always being there for us,\\during the good times but also during times of need.
As part of our family, there will always be a spot for you in our house.\\Let it be a while until one of us has to organise another reception.
Cedric, no time difference or distance can keep us apart,\\or change our habit of forgetting the world around us during our gaming and conversations. 
놀라운 사람과 최고의 친구가되어 주셔서 감사합니다
Big hugs for my family who supported me (Vanessa, Marilou, Franco, Alain,\\Luc, Malika, Sien, Silke, Liam, Anne, Patrick, Evelyne, Stefaan, Arne, Laure, 
Paul, Gilbert, Linda, Tania, Dorian, Steven, Joke, Lukas, Lise), and often had to miss me at family parties.
To mama and papa Jean Paul, thank you for all your love.\\You gave me a carefree youth and a good set of morals,
and allowed me to study for as long as I liked.\\For all these things and so much more, I can never repay you.
Papa Chris, I always enjoy talking to you, such as the countless\\chess games that we played, and the late night discussions by my bedside.
You made me think for myself and have an opinion of my own.\\At the right time, I will pass on the torch to Remi.
Victor, you're the most adventurous of us three brothers.\\Maybe you don't know yet what life will bring, and that's okay. None of us do.
I enjoy driving other people absolutely nuts with our crazy talk.\\Thanks for all the memes :)
Hendrik, as the one who I always looked up to, I blame you for getting me interested\\in computers. With you taking computers apart on the table, how could I resist.
I know you paid dearly for this, though, since you would continuously have to\\repair the \textit{Windows Me} installation that I just destroyed.
Ingeborg, Elke and Gallina, thank you for your hospitality and tasty food.\\You are all amazing women
for all I know, dealing with a Cannoodt,\\requires a special kind of patience.
Go to the next chapter for more acknowledgements.
